---
title: "Web Scraping in R"
author: "Sahil Singh"
date: "2023-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(ggwordcloud)
```

## Scrape https://www.azlyrics.com/b/beatles.html to find top 10 words

### Code for scraping (do not run)
```{r}
#########################
#  ---RUN ONLY ONCE---  #
#########################

# # Main page
# x <- scan("https://www.azlyrics.com/b/beatles.html", what = "", sep = "\n")
# 
# ## Getting all urls from the main page for each song
# urls <- list()
# for (i in 1:length(x)) {
#   # extract URLs using regular expressions
#   urls[[i]] <- ifelse(grepl('href="/lyrics/beatles', x[i]),
#                       paste0("https://www.azlyrics.com", ## Completing link
#                              gsub('.*href="(/lyrics/beatles.*?)".*',
#                                   '\\1',
#                                   x[i])),
#                       NA)
# }
# urls <- urls[is.na(urls) == F] # Dropping NAs
# 
# ## Getting lyrics from all the urls
# 
# lyrics <- list()
# 
# # Define the time interval in seconds for loop delay
# time_interval <- 330 # 5.5 minutes
# 
# # Running loop at specified time intervals as IP Address updates in background
# for (j in 1:48) {
#   # Scraping each link to extract the lyrics
#   for (i in (length(lyrics)+1):(length(lyrics)+9)) {
#     y <- scan(urls[[i]], what = "", sep = "\n")
#     a <- grep("<!-- Usage of azlyrics.com content by any third-party lyrics provider is prohibited by our licensing agreement. Sorry about that. -->", y)
#     b <- grep("</div>", y[a+1:length(y)])[1] + a
#     slyrics <- y[(a+1):(b-1)]
#     lyrics[[i]] <- lapply(slyrics, function(x) gsub("<br>", "", x))
#   }
#   # Pause the execution of the loop for 5.5 minutes to update IP Address
#   Sys.sleep(time_interval)
# }
# 
# # saving file for future use
# saveRDS(lyrics, file="lyrics")

##########################
# ^^^ DONT RUN AGAIN ^^^ #
##########################
```

Load scraped RDS file (to avoid scraping again and again)
```{r}
lyrics <- readRDS("lyrics")
```

### Finding top ten words

```{r}
mylrc <- lyrics

mylrc <- lapply(mylrc, function(x) {
  # Convert to lowercase
  x <- tolower(x)
  # Remove special characters
  x <- gsub("[^[:alpha:][:space:]]", "", x)
  # Split into words
  x <- unlist(strsplit(x, "\\s+"))
  # Return modified string
  return(x)
})

# Unlist the output
mylrc <- unlist(mylrc)

# Remove empty strings
mylrc <- mylrc[mylrc != ""]

# Scan stop words from "https://gist.githubusercontent.com/sebleier/554280/raw/7e0e4a1ce04c2bb7bd41089c9821dbcf6d0c786c/NLTK's%2520list%2520of%2520english%2520stopwords"
stopwords <- scan("https://gist.githubusercontent.com/sebleier/554280/raw/7e0e4a1ce04c2bb7bd41089c9821dbcf6d0c786c/NLTK's%2520list%2520of%2520english%2520stopwords", 
          what = "", 
          sep = "\n")

# Remove stop words
mylrc <- mylrc[!(mylrc %in% stopwords)]

# Count the number of occurrences of each word
word_counts <- table(mylrc)

# Sort the word counts in descending order
word_counts <- sort(word_counts, decreasing = TRUE)

# Displaying top ten words
word_counts[1:10]
```

### Visualizing the outcome

```{r}
# Converting to dataframe for ease in visualizations
topwords <- data.frame("words" = as.character(names(word_counts)),
                 "counts" = as.numeric(word_counts))
```

#### Bar plot
```{r}
# Horizontal bar plot
ggplot(topwords[1:10,], aes(x = counts, y = words)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  labs(x = "Count", y = "Word", title = "Number of occurrences of top words") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

#### Pie Chart
```{r}
percentages <- round(topwords$counts[1:10]/sum(topwords$counts[1:10])*100, 2)
labels <- paste(topwords$words[1:10], "(", percentages, "%)", sep = "")

pie(topwords$counts[1:10], labels = labels, main = "Word Occurrences")
```

#### Word cloud
```{r}
# Create word cloud using ggplot2
ggplot(topwords[1:100,], aes(label = words, size = counts)) +
  geom_text_wordcloud() +
  scale_size(range = c(2, 10)) +
  theme_minimal()
```

#### New Beatles song using above top 10 words using ChatGPT <br>
<br>

##### Never Gonna Let You Go<br>
Verse 1:<br>
I know you love me, oh can't you see <br>
I'm the one for you, baby just believe<br>
I'm not like the others, don't you know<br>
I'll never let you go, I'll never let you go<br>
<br>
Chorus:<br>
Yeah, yeah, yeah, I got you now<br>
Oh, oh, oh, don't you ever doubt<br>
My love for you is strong, well, you know<br>
I'm never gonna leave, I'm never gonna go<br>
<br>
Verse 2:<br>
Imperfect as I am, you accept me for me<br>
You know all my flaws, yet you still believe<br>
In our love, in our forever<br>
I'm so grateful we're together<br>
<br>
Chorus:<br>
Yeah, yeah, yeah, I got you now<br>
Oh, oh, oh, don't you ever doubt<br>
My love for you is strong, well, you know<br>
I'm never gonna leave, I'm never gonna go<br>
<br>
Bridge:<br>
Sometimes things may get rough<br>
But with you by my side, I'm tough<br>
I can get through anything, don't you see<br>
As long as you're here with me<br>
<br>
Chorus:<br>
Yeah, yeah, yeah, I got you now<br>
Oh, oh, oh, don't you ever doubt<br>
My love for you is strong, well, you know<br>
I'm never gonna leave, I'm never gonna go<br>
<br>
Outro:<br>
I love you, baby, with all my heart<br>
And I promise, we'll never be apart<br>
So just hold on tight, and never let go<br>
'Cause together, we'll weather any storm, well, you know.<br>